### 2015-04-08 store-opsem.tex
Fixed typos

Figure ~\ref{sem:oper} presents operational semantics as rules
defining the reduction relation ($\xrightarrow{}$) over the execution
state.  Since we now have a concrete store, we extend our system model
with $\Theta$, a representation of the store as a map from replicas to
their local states. The local state of a replica $r$ (i.e.,
$\Theta(r)$) is a set of effects that are currently visible at $r$.
An operation $op$ performed at replica $r$ can only witness the set of
effects ($\Theta(r)$) visible at $r$. To avoid too many paranthesis in
our formal presentation, we represent operation $op$, whose contract
is in consistency class $\tau$, as $op_\tau$ instead of the usual
$\langle op,\tau \rangle$. For the sake of clarity, we only
consider a single replicated object of well-defined type (for eg: a
replicated object of type \cf{BankAccount}) in our formalization.  Our
semantics are parametric over the specification of this replicated
data type. Figure~\ref{sem:oper} formalizes replicated data type (RDT)
specification as tuple $(\delta,\Ops,\Ctrts)$, where $\delta$ is the
data type, $\Ops$ maps labels ($op$) of operations on $\delta$ to
their definitions, while $\Ctrts$ maps them to their consistency
contracts ($\cv$). The definition of an operation is expected to be a
lambda expression, although we do not enforce this in our
formalization. For technical reasons, we tag each session with a
session identifier ($s$) and the sequence number ($i$) of the next
operation in the session.

@@

Basic gurantee provided by the store is causal visibility, which is
captured by the rule $\rulelabel{EffVis}$ as a condition for an effect
to be visible at a replica. The rule makes an effect ($\eff$) visible
at a replica $r$ only after all the effects that causally precede
$\eff$ are made visible at $r$.  It is important to note that that
enforcing causal visibility does not require any inter-replica
coordination. Any eventually consistent store can provide causal
visibility while being eventually consistent.  Therefore, we do not
lose any generality by assuming that the store provides causal
visiblity.

>>>>

Figure ~\ref{sem:oper} presents operational semantics as rules
defining the reduction relation ($\xrightarrow{}$) over the execution
state.  Since we now have a concrete store, we extend our system model
with $\Theta$, a representation of the store as a map from replicas to
their local states. The local state of a replica $r$ (i.e.,
$\Theta(r)$) is a set of effects that are currently visible at $r$.
An operation $op$ performed at replica $r$ can only witness the set of
effects ($\Theta(r)$) visible at $r$. To avoid too many parentheses in
our formal presentation, we represent operation $op$, whose contract
is in consistency class $\tau$, as $op_\tau$ instead of the usual
$\langle op,\tau \rangle$. For the sake of clarity, we only
consider a single replicated object of well-defined type (for eg: a
replicated object of type \cf{BankAccount}) in our formalization.  Our
semantics are parametric over the specification of this replicated
data type. Figure~\ref{sem:oper} formalizes replicated data type (RDT)
specification as tuple $(\delta,\Ops,\Ctrts)$, where $\delta$ is the
data type, $\Ops$ maps labels ($op$) of operations on $\delta$ to
their definitions, while $\Ctrts$ maps them to their consistency
contracts ($\cv$). The definition of an operation is expected to be a
lambda expression, although we do not enforce this in our
formalization. For technical reasons, we tag each session with a
session identifier ($s$) and the sequence number ($i$) of the next
operation in the session.

@@

Basic guarantee provided by the store is causal visibility, which is
captured by the rule $\rulelabel{EffVis}$ as a condition for an effect
to be visible at a replica. The rule makes an effect ($\eff$) visible
at a replica $r$ only after all the effects that causally precede
$\eff$ are made visible at $r$.  It is important to note that that
enforcing causal visibility does not require any inter-replica
coordination. Any eventually consistent store can provide causal
visibility while being eventually consistent.  Therefore, we do not
lose any generality by assuming that the store provides causal
visibility.
